### 2023-04-21 doc/definitions.tex
proved unit_ball is a dvr

\begin{lemma}
\label{eq_char_local_field.local_field}
\lean{eq_char_local_field.local_field}
\uses{local_field, eq_char_local_field}
An equal characteristic local field is a local field.
\end{lemma}
\subsection{Ramification Index}
\section{Global to Local}
\begin{proposition}
\label{prop:number_field_localization}
\lean{number_field.adic_completion.mixed_char_local_field}
Let $F$ be a number field and let $v$ be a finite place of residue characteristic $p$. Then $F_v$ is a mixed characteristic local field with residue characteristic $p$.
\end{proposition}

>>>>

\begin{lemma}
\label{eq_char_local_field.local_field}
\lean{eq_char_local_field.local_field}
\uses{local_field, eq_char_local_field}
An equal characteristic local field is a local field.
\end{lemma}
\subsection{Ramification Index}
\begin{enumerate}
\item Define a local ramification index to get rid of the variables $\primeid$ and $\primeid[P]$ in the mathlib definition
\item Obtain from there the formula $n=ef$
\item Prove that $\Qp$ and $\laurentseries$ are unramified
\item If possible, go through \cite[Chap. I, \S6]{Se2} (before completion, the results there hold for DVR's).
\end{enumerate}
\section{Global to Local}
Starting with a Dedekind domain $R$ and a non-zero maximal ideal $\primeid$, let $K=\operatorname{Frac}(R)$. Then we prove the
\begin{proposition}[{\cite[Chap. II, \S2, Théorème 1]{Se2}}]
\label{prop:extension_equal}
\lean{is_dedekind_domain.height_one_spectrum.is_discrete}
The completion $K_{\primeid}$ has a discrete valuation extending the valuation $v_{\primeid}$ and such that $\unitball{K_{\primeid}}=R_{\primeid}$. In particular, this localization is a DVR by Proposition~\ref{prop:unit_ball_dvr}.
\end{proposition}

\begin{proposition}
\label{prop:number_field_localization}
\lean{number_field.adic_completion.mixed_char_local_field}
Let $F$ be a number field and let $v$ be a finite place of residue characteristic $p$. Then $F_v$ is a mixed characteristic local field with residue characteristic $p$.
\end{proposition}
